\documentclass[11pt,a4paper,sans]{moderncv}

%% ModernCV themes
\moderncvstyle{classic}
\moderncvcolor{blue}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

%% Character encoding
\usepackage[utf8]{inputenc}

%% Adjust the page margins
\usepackage[scale=0.75]{geometry}

%% Personal data
\firstname{Eugen}
\familyname{Ciur}
\title{DevOps/SRE Role Application}
\address{Trusetaler str 90}{12687 Berlin, Germany}
\mobile{+49 15736195069}
\email{ciur.eugen@gmail.com}
\homepage{github.com/ciur}


%%------------------------------------------------------------------------------
%% Content
%%------------------------------------------------------------------------------
\begin{document}
    \makecvtitle

    I am Sr. Software Developer with more then 15 years of
    experience. In last 5 years I was mostly
    focused on building web services which use python as main
    back-end language and are deployed in k8s cloud environments.

    \section{Tech Skills}
    \cvdoubleitem{Languages}{Python, Go, TypeScript, C/C++, Java}{Cloud}{AWS, Docker, Kubernetes, Helmcharts, ArgoCD}
    \cvdoubleitem{Web Frameworks}{Django, Flask, FastAPI, Django REST Framework, React, Redux, pytest}{CVS}{git, mercurial, github, gitlab}
    \cvdoubleitem{Databases}{PostgreSQL, Mysql/MariaDB, SQLite}{Other}{REST API, OpenAPI, swagger, CI/CD, websockets}
    \cvdoubleitem{Message Queues}{RabbitMQ, Redis}{Protocols}{TCP/IP, HTTP, IMAP, POP3, SMTP}

    \section{Work Experience}

    \cventry{09.2023 -- 31.10.2024}{Software Developer}{Snom Gmbh}{Berlin}{ Germany }{
      At Snom I, together with my team, developed internal web application for testing phones' firmware.
      This means we developed application backend and frontend and deployed it in our internal Proxmox.
      Technically speaking, application' backend is in Python/Django/RQ. Frontend in React.
      Deployment was performed using ansible roles (which started docker images on remove VMs).
      Deployment was triggered via Jenkins jobs. Application's authentication was based on company's internal LDAP.
      Our team was responsable for infracture as well (i.e. we managed proxmox and VMs in it).
      }

    \cventry{11.2022 -- 09.2023}{Team Lead}{IONOS Cloud}{Berlin}{ Germany }{
      In my team lead role I manage a small team of four persons
        which consists of two developers, one QA engineer and me.
        We use SCRUM as base framework for organizing our
        development process. Our team is responsible for maintaining
        two internal web services (Django and Flask based
        respectively). Technically speaking, application was classical all-backend based Python/Django/Celery
        (i.e. no react frontend). Application was deployed in company's internal k8s cluster.
        Our team was in charge of app's Helmcharts. Internally app had a prometheus endpoint
        which was scraped into our internal grafana/loki and used for app monitoring and performance tuning.
      }

   \vspace{0.4cm}

    \cventry{05.2021 -- 11.2022}{Sr. Python Developer}{IONOS Cloud}{Berlin}{ Germany }{
      In was in charge of development, maintenance and deploymment of two internal applications - one Django based,
      another one Flask based (with ReactJS frontend).
      I was part of moving deployment method from classical VM based with Ansible to modern cloud native Kubernetes based
      (with its own Helmchart and ArgoCD syncing).
     }

    \vspace{0.4cm}

    \cventry{12.2019 -- present}{Self Employed}{max. 4 hours/week}{Berlin}{ Germany }
    {
      Development and promotion of open source DMS for digital archives. Technically, Papermerge DMS
      is cloud native application - which means it designed to be deployed in k8s environments and
      monitored using prometheus KPI. It uses SOLR as search engine. It can be
      integrated with external authentication systems like Keycloak.
    }

    \cvitem{homepage}{\url{https://papermerge.com}}
    \cvitem{main repo}{\url{https://github.com/ciur/papermerge}}
    \cvitem{documentation}{\url{https://docs.papermerge.io}}
    \cvitem{github org}{\url{https://github.com/papermerge}}

  \vspace{0.4cm}

    \cventry{12.2018 -- 12.2020}{Django Lessons}{Youtuber}{Berlin}{ Germany } {
        I recorded 51 Python/Django/Development/Deployment youtube screencasts which were (and are) relatively popular.
    }


    \cvitem{YT}{\url{https://www.youtube.com/@djangolessons4614}}

    \vspace{0.4cm}

    \cventry{12.2012 -- 11.2018}{Software Engineer}{Oracle}{Berlin}{ Germany }{
        I was in charge of maintenance and development web application which served
        as front-end for a larger VoIP Monitoring solution used
        by hundreds big telcoms and service providers. Mostly I
        dealt with Python based back-end and JavaScript/CSS/HTML based front-
        end. Fullstack web application was written in custom i.e.
        in-house web framework.
    }

  \vspace{0.4cm}

    \cventry{01.2012 -- 06.2012}{RubyOnRails Developer}{Mediapeers}{Berlin}{ Germany }{
        In this role I maintained a full-stack web application based
        on RubyOnRails web framework. Product was web application for management of
        media content.
    }

  \vspace{0.4cm}

    \cventry{11.2009 -- 11.2011}{R\&D Engineer}{PrimeTel}{Limassol}{ Cyprus}{
        During my research activity at PrimeTel I led development of
        IPTV commerce solution (in RubyOnRails): IPTV
        COMMERCE is a nationally funded by the Cyprus Research
        Promotion Foundation project. The project dealt with the study
        of required infrastructure on the support of total of services via
        the IPTV platform.
    }

  \vspace{0.4cm}

    \cventry{12.2007 -- 11.2009}{SME Software Developer}{Amdocs}{Limassol}{ Cyprus}{
        Various projects in C/C++/Java/SQL
    }

    \section{Education}
    \cventry{2002--2007}{Computer Science}{Universitatea Politehnica din București}{Bucharest}{Romania}{
        At Politech University in Bucharest I completed computer science degree
    }

    \cventry{1998--2001}{Informatics}{High School with focus on Math and Informatics}{Chișinău}{Moldova}{}

    \section{Languages}

    \cvitemwithcomment{English}{Fluent}{}
    \cvitemwithcomment{Romanian}{Native}{}
    \cvitemwithcomment{German}{C1}{Can read, write, understand well - but not much experience in speaking}
    \cvitemwithcomment{Spanish}{A1}{currently learning}

  \section{Extras}

  \begin{itemize}
    \item 2002 - I won silver medal at 19-th Balkan Mathematical Olympiad, Antalya, Turkey
    \item 2002 - I won 2nd National Prize at Math Olympiad (ro: Olimpiada Republicană de Matematică, Moldova)
    \item 2001 - I won 3rd National Prize at Math Olympiad (ro: Olimpiada Republicană de Matematică, Moldova)
  \end{itemize}

\end{document}
